---
title: "Optimum Guess Calculator for Reddit Random Number Giveaways"
author: "Paul Foster"
date: "5 April 2016"
output: github_document
---

### Overview
Various Reddit giveaway posts involve the poster randomly choosing a number and the commenter who comments the number closest to this is the winner. See [this post](https://www.reddit.com/r/RandomActsOfGaming/comments/4d65cb/giveaway_south_park_the_stick_of_truth_steam_key/) for an example of a giveaway post.

This code is used to calculate the optimal guess by finding the middle of the biggest gap in the guesses. It downloads all the comments, extracts the numbers, plots the density of guesses and outputs the optimum number to guess.


### Inputs
To apply the analysis to any post, simply modify three variables: `MIN_GUESS`, `MAX_GUESS` and `POST_URL`.

```{r}
MIN_GUESS <- 0
MAX_GUESS <- 999
POST_URL <- 'https://www.reddit.com/r/RandomActsOfGaming/comments/4d65cb/giveaway_south_park_the_stick_of_truth_steam_key/'
```


### Outputs
<!-- Generate the smoothed data -->
```{r, echo=FALSE, results='hide', message=FALSE, warning=FALSE}
if (!require('pacman'))
    install.packages('pacman')

pacman::p_load('ggplot2',
               'RedditExtractoR',
               'tidyr')

comment_data <- reddit_content(POST_URL)

guessed_numbers <- comment_data$comment %>%
    unlist %>%
    strsplit('[^0-9]+') %>%
    unlist %>%
    as.numeric %>%
    na.omit %>%
    unique %>%
    sort

smoothed <- density(guessed_numbers, adjust=0.1)
smoothed <- data.frame(x=smoothed$x, y=smoothed$y)

guess_df <- data.frame(number=seq(from=MIN_GUESS, to=MAX_GUESS, by=1))
guess_df$is_guessed <- guess_df$number %in% guessed_numbers

run_lengths <- rle(guess_df$is_guessed) %>%
    unclass %>%
    data.frame

only_false_lengths <- ifelse(!run_lengths$values, run_lengths$lengths, 0)
longest_false_run_index <- which.max(only_false_lengths)
longest_false_run_length <- only_false_lengths[longest_false_run_index]

start_of_longest_gap <- cumsum(run_lengths$lengths)[longest_false_run_index-1]
end_of_longest_gap <- start_of_longest_gap + longest_false_run_length

best_guess <- (start_of_longest_gap + end_of_longest_gap - 1) %/% 2
```

#### 1D Density Plot of the Guessed Numbers 
Darker sections indicate larger gaps in guesses.

```{r echo=FALSE, warning=FALSE}
ggplot(smoothed, aes(x=x, y=1, fill=y)) +
    labs(title='Density of Guessed Numbers',
         y='',
         x='Guessed Number') +
    theme(axis.ticks=element_blank(), axis.text.y=element_blank()) +
    xlim(MIN_GUESS, MAX_GUESS) +
    scale_fill_continuous(name='Density') +
    geom_tile()
```


#### 2D Density Plot of the Guessed Numbers 
Lower points indicate larger gaps in guesses.
```{r echo=FALSE, warning=FALSE}
ggplot(data.frame(number=guessed_numbers), aes(x=number, fill=1)) +
    labs(title='Density of Guessed Numbers',
         y='Density',
         x='Guessed Number') +
    theme(legend.position = "none") +
    geom_density(adjust=0.1)
```

#### Optimal Number to Guess

```{r echo=FALSE}
message('The best new guess that can be made is ',
        best_guess,
        ' which covers ',
        longest_false_run_length %/% 2,
        ' numbers.')
```















